Pillar 1 - Sequential Pattern Mining

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
knit updated
to do list

### CSPADE Algorithm
```{r function clean SR}
# Transform rules from ruleInduction into a readable data frame
n_students <- length(unique(d_transactions$sequenceID))

@@

```
We apply cspade followed by rule induction
```{r cspade and rule induction, cache = TRUE}
# Run the cspade algorithm with desired parameters. Then run the ruleInduction algorithm with desired parameters.
my_SR<- function(data){
 data %>%
  cspade(
    parameter = list(
      support = 0, # min support of a sequence
      maxsize = 1, # max number of items of an element of a sequence
      maxlen  = 2, # max number of element of a sequence
      mingap  = 1, # min time difference between consecutive element of a sequence
      maxgap  = 1e4 # max time difference between consecutive element of a sequence
      #maxwin  = 1e4  # max time difference between any two elements of a sequence # WARNING: 'maxwin' disabled
      ),
    control = list(
      verbose = FALSE
      )
    ) %>%
    ruleInduction(
      confidence = 0, #we need to play with the parameters.
      control    = list(verbose = FALSE)
      ) %>%
    clean_SR
}

>>>>

### CSPADE Algorithm
##TODO: FILTER FAILS AND LOW GRADE
Change name confidence corrected to confidence, confidence to confidence old, same for lift
```{r function clean SR}
# Transform rules from ruleInduction into a readable data frame
n_students <- length(unique(d_transactions$sequenceID))

@@

```
We apply cspade followed by rule induction
```{r cspade and rule induction, cache = F}
# Run the cspade algorithm with desired parameters. Then run the ruleInduction algorithm with desired parameters.
my_SR<- function(data){
 data %>%
  cspade(
    parameter = list(
      support = 0, # min support of a sequence
      maxsize = 1, # max number of items of an element of a sequence
      maxlen  = 2, # max number of element of a sequence
      mingap  = 1, # min time difference between consecutive element of a sequence
      maxgap  = 1e4 # max time difference between consecutive element of a sequence
      #maxwin  = 1e4  # max time difference between any two elements of a sequence # WARNING: 'maxwin' disabled
      ),
    control = list(
      verbose = FALSE
      )
    ) %>%
    ruleInduction(
      confidence = 0, #we need to play with the parameters.
      control    = list(verbose = FALSE)
      ) %>%
    clean_SR
}
